### 2017-10-08 manuscript.rmd
added p values to correlation coefficients

	# Calculate some summary statistics 
	ortholog_r = 
		pairwise_summary %>% 
		filter( D=="N" ) %>% 
		select( tau_a, tau_b ) %>% 
		cor( ) %>% 
		.[ 1, 2 ]

	paralog_r = 
		pairwise_summary %>% 
		filter( D=="Y" ) %>% 
		select( tau_a, tau_b ) %>% 
		cor( ) %>% 
		.[ 1, 2 ]

	paralog_subset_r = 
		pairwise_summary %>% 
		filter( D=="Y" ) %>% 
		filter( node_age <= max_speciation_age ) %>% 
		select( tau_a, tau_b ) %>% 
		cor( ) %>% 
		.[ 1, 2 ]

@@

In order to better understand why our phylogenetic analysis supports a different conclusion (*i.e.*, no support for the ortholog conjecture) than the published analysis of KMRR [@KryuchkovaMostacci:2016iw] (*i.e.*, strong support for the ortholog conjecture), we first checked to make sure we could reproduce their result based on pairwise analyses. This is important since we are only looking at a subset of the data they considered, the Brawand *et al.* 2011 [@Brawand:2011du] dataset for gene trees that could be successfully time calibrated. In their Fig. 1 [@KryuchkovaMostacci:2016iw], they present a higher Tau correlation coefficient between ortholog pairs than paralog pairs. We find the same here, with correlation coefficients of `r signif( ortholog_r, 2)` for orthologs and `r signif( paralog_r, 2)` for paralogs.

@@

To test the hypothesis that ancient duplications that precede the oldest speciation event (*SI Appendix*, Fig. 5*A*) impact the lower correlation of Tau between paralogs than between orthologs, we removed them. When we consider only the duplication events the same age or younger than the oldest speciation event (*SI Appendix*, Fig. 5*B*), the paralog correlation coefficient increases from `r signif( paralog_r, 2)` to `r signif( paralog_subset_r, 2)`. This is much closer to the ortholog correlation of `r signif( ortholog_r, 2) `.

@@

	# Calculate some summary statistics 
	ortholog_r_sim_null = 
		pairwise_sim_null_summary %>% 
		filter( D=="N" ) %>% 
		select( tau_a, tau_b ) %>% 
		cor( ) %>% 
		.[ 1, 2 ]

	paralog_r_sim_null = 
		pairwise_sim_null_summary %>% 
		filter( D=="Y" ) %>% 
		select( tau_a, tau_b ) %>% 
		cor( ) %>% 
		.[ 1, 2 ]

@@

	ortholog_r_sim_oc = 
		pairwise_sim_oc_summary %>% 
		filter( D=="N" ) %>% 
		select( tau_a, tau_b ) %>% 
		cor( ) %>% 
		.[ 1, 2 ]

	paralog_r_sim_oc = 
		pairwise_sim_oc_summary %>% 
		filter( D=="Y" ) %>% 
		select( tau_a, tau_b ) %>% 
		cor( ) %>% 
		.[ 1, 2 ]

@@

To better understand this plot (Fig. 2*A*), we performed simulations of Tau on the calibrated gene trees. We did not modify the gene tree topologies or their inferred histories of duplication and loss. First, we simulated the evolution of Tau under the null model that it evolves at the same rate following duplication and speciation events. Under the null model, the plot of correlation coefficient to node age (Fig. 2*C*) is very similar as for the observed data (Fig. 2*A*). As in the original study, there is higher correlation coefficient across orthologs (`r signif( ortholog_r_sim_null, 2 )`) than paralogs (`r signif( paralog_r_sim_null, 2 )`) when not considering node age. Phylogenetic analysis of the data simulated under the null hypothesis (Fig. 2*D*) do not reject the null hypothesis (Wilcoxon p = $`r wilcox_oc( nodes_sim_null_contrast ) %>% round( 3 )`$), as expected.

We next simulated the evolution of Tau under the ortholog conjecture, where the rate of evolution of Tau following duplication was `r dup_adjust` fold the rate following speciation. The pairwise results of this heterogeneous model (Fig. 2*E*) are nearly indistinguishable from the results under the null model (Fig. 2*C*), and also have a higher correlation coefficient for orthologs (`r signif( ortholog_r_sim_oc, 2 )`) than paralogs (`r signif( paralog_r_sim_oc, 2 )`). The phylogenetic analysis of the ortholog conjecture simulation (Fig. 2*F*) does reject the null hypothesis (Wilcoxon p = $`r signif( wilcox_oc( nodes_sim_oc_contrast ), 2 )`$).

>>>>

	# Calculate some summary statistics 
	ortholog_r = 
		pairwise_summary %>% 
		filter( D=="N" ) %$% 
		cor.test( tau_a, tau_b )

	paralog_r = 
		pairwise_summary %>% 
		filter( D=="Y" ) %$% 
		cor.test( tau_a, tau_b )

	paralog_subset_r = 
		pairwise_summary %>% 
		filter( D=="Y" ) %>% 
		filter( node_age <= max_speciation_age ) %$% 
		cor.test( tau_a, tau_b )

@@

In order to better understand why our phylogenetic analysis supports a different conclusion (*i.e.*, no support for the ortholog conjecture) than the published analysis of KMRR [@KryuchkovaMostacci:2016iw] (*i.e.*, strong support for the ortholog conjecture), we first checked to make sure we could reproduce their result based on pairwise analyses. This is important since we are only looking at a subset of the data they considered, the Brawand *et al.* 2011 [@Brawand:2011du] dataset for gene trees that could be successfully time calibrated. In their Fig. 1 [@KryuchkovaMostacci:2016iw], they present a higher Tau correlation coefficient between ortholog pairs than paralog pairs. We find the same here, with correlation coefficients of `r signif( ortholog_r$estimate, 2)` (p `r format_p(ortholog_r)`) for orthologs and `r signif( paralog_r$estimate, 2)` (p `r format_p( paralog_r )`) for paralogs.

@@

To test the hypothesis that ancient duplications that precede the oldest speciation event (*SI Appendix*, Fig. 5*A*) impact the lower correlation of Tau between paralogs than between orthologs, we removed them. When we consider only the duplication events the same age or younger than the oldest speciation event (*SI Appendix*, Fig. 5*B*), the paralog correlation coefficient increases from `r signif( paralog_r$estimate, 2)` to `r signif( paralog_subset_r$estimate, 2)` (p `r format_p(paralog_subset_r)`). This is much closer to the ortholog correlation of `r signif( ortholog_r$estimate, 2) `.

@@

	# Calculate some summary statistics 
	ortholog_r_sim_null = 
		pairwise_sim_null_summary %>% 
		filter( D=="N" ) %$% 
		cor.test( tau_a, tau_b )

	paralog_r_sim_null = 
		pairwise_sim_null_summary %>% 
		filter( D=="Y" ) %$% 
		cor.test( tau_a, tau_b )

@@

	ortholog_r_sim_oc = 
		pairwise_sim_oc_summary %>% 
		filter( D=="N" ) %$% 
		cor.test( tau_a, tau_b )

	paralog_r_sim_oc = 
		pairwise_sim_oc_summary %>% 
		filter( D=="Y" ) %$% 
		cor.test( tau_a, tau_b )

@@

To better understand this plot (Fig. 2*A*), we performed simulations of Tau on the calibrated gene trees. We did not modify the gene tree topologies or their inferred histories of duplication and loss. First, we simulated the evolution of Tau under the null model that it evolves at the same rate following duplication and speciation events. Under the null model, the plot of correlation coefficient to node age (Fig. 2*C*) is very similar as for the observed data (Fig. 2*A*). As in the original study, there is higher correlation coefficient across orthologs (`r signif( ortholog_r_sim_null$estimate, 2 )`, p `r format_p(ortholog_r_sim_null)`) than paralogs (`r signif( paralog_r_sim_null$estimate, 2 )`, p `r format_p(paralog_r_sim_null)`) when not considering node age. Phylogenetic analysis of the data simulated under the null hypothesis (Fig. 2*D*) do not reject the null hypothesis (Wilcoxon p = $`r wilcox_oc( nodes_sim_null_contrast ) %>% round( 3 )`$), as expected.

We next simulated the evolution of Tau under the ortholog conjecture, where the rate of evolution of Tau following duplication was `r dup_adjust` fold the rate following speciation. The pairwise results of this heterogeneous model (Fig. 2*E*) are nearly indistinguishable from the results under the null model (Fig. 2*C*), and also have a higher correlation coefficient for orthologs (`r signif( ortholog_r_sim_oc$estimate, 2 )`, p `r format_p( ortholog_r_sim_oc )`) than paralogs (`r signif( paralog_r_sim_oc$estimate, 2 )`, p `r format_p( paralog_r_sim_oc )`). The phylogenetic analysis of the ortholog conjecture simulation (Fig. 2*F*) does reject the null hypothesis (Wilcoxon p = $`r signif( wilcox_oc( nodes_sim_oc_contrast ), 2 )`$).
